Testing the precision of Bangla Communication Scale: Item Response Theory Guided Analysis

### 2022-02-04 manuscript.Rmd
Title Corrected

---
title             : "Psychometric Evaluation of the Bangla-translated Rotter Internal-External Scale through Classical Test Theory and Item Response Theory"
shorttitle        : "Bangla Communication Scale"

author: 
  - name          : "Nusrat Jahan"
    affiliation   : "1"
    corresponding : no    # Define only one corresponding author
    role:         
      - Conceptualization
      - Data Curation
      - Writing - Original Draft Preparation
  - name          : "Mushfiqul Anwar Siraji"
    affiliation   : "2"
    corresponding : no   # Define only one corresponding author
    address       : "Monash University Malaysia,Jalan Lagoon Selatan, 47500 Bandar Sunway,Selangor Darul Ehsan, Malaysia."
    email         : "mushfiqul.anwarsiraji@moansh.edu"
    role:
      - Conceptualization
      - Project Management
      - Formal Analysis
      - Data Visualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing

  - name          : "Zinnatul Borak"
    affiliation   : "1"
    corresponding : yes   # Define only one corresponding author
    address       : "Department of Educational and Counselling Psychology,University of Dhaka,Dhaka 1000"
    email         : "mushfiqul.anwarsiraji@moansh.edu"
    role:
      - Conceptualization
      - Writing - Review & Editing

>>>>

---
title             : "Psychometric Evaluation of the Bangla Communication Scale through Classical Test Theory and Item Response Theory"
shorttitle        : "Bangla Communication Scale"

author: 
  - name          : "Nusrat Jahan"
    affiliation   : "1"
    corresponding : no    # Define only one corresponding author
    role:         
      - Conceptualization
      - Project Management
      - Data Curation
      - Writing - Original Draft Preparation
  - name          : "Mushfiqul Anwar Siraji"
    affiliation   : "2"
    corresponding : no   # Define only one corresponding author
    address       : "Monash University Malaysia,Jalan Lagoon Selatan, 47500 Bandar Sunway,Selangor Darul Ehsan, Malaysia."
    email         : "mushfiqul.anwarsiraji@moansh.edu"
    role:
      - Conceptualization
      - Project Management
      - Formal Analysis & Data Visualization
      - Writing - Original Draft Preparation; Review & Editing

  - name          : "Zinnatul Borak"
    affiliation   : "1"
    corresponding : yes   # Define only one corresponding author
    address       : "Department of Educational and Counselling Psychology,University of Dhaka,Dhaka 1000"
    email         : "institutional email of Bonhee mam"
    role:
      - Conceptualization
      - Writing - Review & Editing
